%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Autonomous Navigation Engineer} % Job title
    {United Robots} % Organization
    {Warsaw, Poland} % Location
    {August 2023 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Served as team lead for SLAM team.}
        \item {Integrated AruCo marker detection for landmark based SLAM algortihms.}
        \item {Developed new features for Google cartographer SLAM algortihm for indoor robotics solutions.}
        \item {Led the development and execution of extensive testing methodologies for new software features and sensor integrations.}
        \item {Integrated unit tests on the robot software suite.}
        \item {Performed live testing of robots at customer's facilities.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {Wärtsilä Voyage} % Organization
    {Leicester, UK} % Location
    {August 2021 - July 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Improved quay detection with radar performance in vessel docking operations by 20\%.}
        \item {Developed radar based SLAM for inland waterway vessel operations for GNSS redundancy.}
        \item {Led DevOps migration to Git via development of automation tools and training.}
        \item {Supported customers with troubleshooting.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Autonomous Robotics Software Engineer} % Job title
    {Dynium} % Organization
    {Oxford, UK} % Location
    {December 2018 - August 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed software for different sensor modules, such as lidars, ultrasound, IMU, that are used for path planning and obstacle avoidance such
        as ultrasonics, IMU.}
        \item {Designed and tested ultrasound sensor module software and PCBs.}
        \item {Developed custom CAN and handshake protocol for team’s requirements.}
        \item {Designed robot hardware and software test rig for local testing of software.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
